Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-08 csf-2017/paper.tex
comment

\emph{Capability machines} are a type of processors, intended to remediate these
limitations by presenting a better security model at the hardware
level~\cite{Watson2015Cheri,Woodruff:2014:CCM:2665671.2665740,Carter:1994:HSF:195473.195579}.\dominique{todo:
  more?} Such hardware tags every word (in the register file and in memory) to
enforce a strict separation between numbers and capabilities, a kind of pointers
carrying some kind of authority. Memory capabilities carry the authority to read
and/or write to a range of memory locations. Additionally, the details vary but
all capability machines offer some form of \emph{object capabilities}, which
represent the authority to invoke a piece of code without exposing the code's
encapsulated private state (e.g. the M-Machine's enter capabilities or CHERI's
sealed code/data pairs).

>>>>

\emph{Capability machines} are a type of processors, intended to remediate these
limitations by presenting a better security model at the hardware
level~\cite{Watson2015Cheri,Woodruff:2014:CCM:2665671.2665740,Carter:1994:HSF:195473.195579}.\dominique{todo:
  more?} \lars{can we add that there has been renewed interest and
  refer to crash-safe project ?}
 Such hardware tags every word (in the register file and in memory) to
enforce a strict separation between numbers and capabilities, a kind of pointers
carrying some kind of authority. Memory capabilities carry the authority to read
and/or write to a range of memory locations. Additionally, the details vary but
all capability machines offer some form of \emph{object capabilities}, which
represent the authority to invoke a piece of code without exposing the code's
encapsulated private state (e.g. the M-Machine's enter capabilities or CHERI's
sealed code/data pairs).
